% Document class and font size
\documentclass[a4paper,9pt]{extarticle}

% Packages
\usepackage[utf8]{inputenc} % For input encoding
\usepackage{geometry} % For page margins
\geometry{letterpaper, margin=0.75in} % Set paper size and margins
\usepackage{titlesec} % For section title formatting
\usepackage{enumitem} % For itemized list formatting
\usepackage{hyperref} % For hyperlinks
\usepackage{tabularx}
\usepackage{fancyhdr}
\usepackage{fontawesome5}
\usepackage{hanging}
 \usepackage{setspace}

% Formatting
\setlist{noitemsep} % Removes item separation
\titleformat{\section}{\large\bfseries}{\thesection}{1em}{}[\titlerule] % Section title format
\titlespacing*{\section}{0pt}{\baselineskip}{\baselineskip} % Section title spacing
%%%%%%%%%%
\setstretch{1.22}

% Begin document
\begin{document}

% Disable page numbers
\pagestyle{fancy}
\renewcommand{\headrulewidth}{0pt}
\fancyhead{}
\fancyhead[L]{\textit{Doron Haviv}}
\fancyhead[R]{\textit{Updated April 2026}}
\thispagestyle{empty} % Remove header from the first page

% Header
\begin{center}
    \textbf{\Huge \scshape Doron Haviv} \\ 
    \Large{Research Scientist at Genentech} \\ 
    \small
    \vspace{4pt} 
        \faIcon{envelope}
    \href{mailto:doron.haviv12@gmail.com}
    {\underline{doron.haviv12@gmail.com}}  $  $
    \faIcon{graduation-cap}
    \href{https://scholar.google.com/citations?user=tWeeha4AAAAJ&hl=en&oi=ao}{\underline{Doron Haviv}} $  $
    \faIcon{linkedin}
    \href{https://www.linkedin.com/in/doron-haviv-92ab63138/}{\underline{linkedin.com/in/doron-haviv}} $  $
    \faIcon{globe}
    \href{https://doronhav.github.io}{\underline{doronhav.github.io}}
\end{center}


\section*{EMPLOYMENT}
\noindent
\textbf{Genentech} \footnotesize{BRAID - Biology Research | AI Development} \vspace{2pt} \hfill May 2025 – Present \\
\normalsize{Research Scientist - Spatial Genomics}

% Education Section
\section*{EDUCATION}
\noindent
\textbf{Cornell University} \footnotesize{Joint Memorial Sloan Kettering Cancer Center} \vspace{2pt} \hfill July 2019 – April 2025 \\
\normalsize{Ph.D. in Computational Biology and Medicine\vspace{4pt}} \\ 
\indent Research Advisor: Dana Pe’er \\
\indent Thesis: From Cells to Niche - The Geometry of Spatial Transcriptomics \\

\noindent\\
\normalsize{\textbf{Technion - Israel Institute of Technology}\vspace{2pt}}   \hfill \footnotesize{October 2014 – October 2018}\\ 
\normalsize{B.Sc. Electrical Engineering (\textit{cum laude})\vspace{4pt}}\\
\normalsize{B.Sc. Physics (\textit{cum laude})\vspace{4pt}}\\
\indent Research Advisor: Omri Barak \\
\indent Thesis: Understanding and Controlling Memory in Recurrent Neural Networks. \\

\section*{RESEARCH INTERESTS}
\noindent
generative models, single-cell genomics, optimal transport, spatial transcriptomics

\section*{PUBLICATIONS AND PRE-PRINTS}
\begin{hangparas}{.25in}{1}

\normalsize{\underline{Haviv, D.*}, De Brouwer, E.*, Rishabh, A., Ying, R., Scalia, G., Corrada-Bravo, H. 2026. When Riemann flows with Wasserstein: Generative Modeling of Probability Distributions on Manifolds. \textit{In Review}\\



\normalsize Andersson, A.*, Ismail, A.A.*, De Brouwer, E.*, \underline{Haviv, D.*}, Biancalani, T., Cho, K., Scalia, G., BenTaieb, A., Corrada-Bravo, H. 2025. scCBGM: Single-Cell Editing via Concept Bottlenecks. \textit{In Review}\\


\underline{Haviv, D.*}, Pooladian, A.A.*, Pe'er, D., Amos, B. 2025. Wasserstein Flow Matching: Generative modeling over families of distributions. Proceedings of the 42st International Conference on Machine Learning, PMLR.\\

\underline{Haviv, D.}, Kunes, R.Z., Dougherty, T. Burdziak, C., Nawy T., Gilbert A., Pe'er, D. 2024. Wasserstein Wormhole: Scalable Optimal Transport Distance with Transformers. Proceedings of the 41st International Conference on Machine Learning, PMLR 235:17697-17718.\\

\underline{Haviv, D.}, Remšík, J., Gatie, M., Snopkowski, C., Takizawa, M., Pereira, N., ..., Pe’er, D. 2024. The covariance environment defines cellular niches for spatial inference. Nature Biotechnology, 1-12.\\
\textbf{*Highlighted in \href{https://www.nature.com/articles/s41587-024-02207-1}{\textit{Nature Biotechnology Research Briefing}}}\\

Mani, S.*, \underline{Haviv, D.*}, Kunes, R., Pe'er, D. 2022. SPOT: Spatial Optimal Transport for Analyzing Cellular Microenvironments. In NeurIPS 2022 Workshop on Learning Meaningful Representations of Life.\\
\textbf{*Spotlight Presentation}\\

Elad, A.*, \underline{Haviv, D.*}, Blau, Y. and Michaeli, T., 2019. Direct validation of the information bottleneck principle for deep nets. In Proceedings of the IEEE/CVF International Conference on Computer Vision Workshops.\\
\textbf{*Best poster award Statistical Deep Learning in Computer Vision Workshop}\\

\underline{Haviv, D.}, Rivkind, A. and Barak, O., 2019. Understanding and controlling memory in recurrent neural networks. Proceedings of the 36th International Conference on Machine Learning, PMLR 97:2663-2671.\\

Kunes, R.Z., Yin, M., Land, M., \underline{Haviv, D.}, Pe'er, D. and Tavaré, S., 2023, June. Gradient estimation for binary latent variables via gradient variance clipping. In Proceedings of the AAAI Conference on Artificial Intelligence (Vol. 37, No. 7, pp. 8405-8412).\\

Burdziak, C.*, Zhao, C. J.*, \underline{Haviv, D.}, Alonso-Curbelo, D., Lowe, S. W.,  Pe’er, D. 2023. scKINETICS: inference of regulatory velocity with single-cell transcriptomics data. Bioinformatics, 39(39 Suppl 1), i394–i403. \\
\textbf{*Best paper award Intelligent Systems for Molecular Biology (ISMB) 2023.}\\

Burdziak, C.*, Alonso-Curbelo, D.*, Walle, T., Reyes, J., Barriga, F. M., \underline{Haviv, D.}, Xie, Y., Zhao, Z., Zhao, C. J., Chen, H.-A., Chaudhary, O., Masilionis, I., Choo, Z.-N., Gao, V., Luan, W., Wuest, A., Ho, Y.-J., Wei, Y., Quail, D. F., … Pe’er, D. 2023. Epigenetic plasticity cooperates with cell-cell interactions to direct pancreatic tumorigenesis. Science, 380(6645), eadd5327. \\
\textbf{*Highlighted in \href{https://aacrjournals.org/cancerdiscovery/article-abstract/13/7/1510/727607/Plasticity-Drives-Tumorigenic-Epithelial-Immune?redirectedFrom=fulltext}{\textit{Cancer Discovery}}, \href{https://www.nature.com/articles/s41575-023-00806-y}{\textit{Nature Reviews Gastroenterology and Hepatology}}, \href{https://www.cell.com/trends/cancer/fulltext/S2405-8033(23)00130-9?dgcid=raven_jbs_aip_email}{\textit{Cell Trends in Cancer}}, and \href{https://magazine.eacr.org/highlights-in-cancer-research-august-2023/}{EACR Highlights in Cancer Research}.}\\


Raayoni, G., Gottlieb, S., Manor, Y., Pisha, G., Harris, Y., Mendlovic, U., \underline{Haviv, D.}, Hadad, Y. and Kaminer, I., 2021. Generating conjectures on fundamental constants with the Ramanujan Machine. Nature, 590(7844), pp.67-73.\\
\textbf{*Highlighted in \href{https://www.newscientist.com/article/2209213-computer-attempts-to-replicate-the-dream-like-maths-of-ramanujan/}{\textit{New Scientist}}}\\

}

\end{hangparas}



% Projects Section
\section*{AWARDS AND HONORS}
\noindent
\normalsize
\textbf{Best Poster Award}, SDL-VC workshop, International Conference on Computer Vision	\hfill 2019 \\
Yehoraz Kasher Prize \textbf{Best Student Project in Electrical Engineering, 3rd Place} 	\hfill 2018 \\
Technion - Israel Institute Of Technology \textbf{President's List}	\hfill 2018 \\
Technion - Israel Institute Of Technology \textbf{Dean's List}	\hfill 2017 \\
Technion - Israel Institute Of Technology \textbf{Dean's List}	\hfill 2016 \\

\section*{INVITED AND CONTRIBUTED TALKS}

\noindent
Apple Machine Learning Research Group, Virtual \hfill  2024 \\
\textbf{Invited Talk}: \textit{Wasserstein Wormhole: Scalable
Optimal Transport Distance with Transformers. }	\\

\noindent
\textit{scverse} Community Meeting, Virtual \hfill  2024 \\
\textbf{Invited Talk}: \textit{Reconstructing spatial context for single cell transcriptomics with ENVI}	\\

\noindent
Department of Computer Science Colloquium, Columbia University, New York, New York, USA \hfill  2024 \\
\textbf{Invited Talk}: \textit{Reconstructing spatial context for single cell transcriptomics with ENVI}	\\

\noindent
Ido Amit Lab, Weizmann Institute of Science, Rehovot, Israel \hfill  2024 \\
\textbf{Invited Talk}: \textit{Reconstructing spatial context for single cell transcriptomics with ENVI}	\\

\noindent
10x Spatial World Tour, New York Genome Center, New York, New York, USA \hfill  2023 \\
\textbf{Invited Talk}: \textit{Reconstructing spatial context for single cell transcriptomics with ENVI}	\\

\noindent
 The Jackson Laboratory for Genomic Medicine, Farmington, Connecticut, USA \hfill 2022\\
\textbf{Invited Talk}: \textit{Reconstructing spatial context for single cell transcriptomics with ENVI}	\\

\noindent
Fusion Conference on Probing Human Disease using Single-Cell Technologies, Cancun, MX \hfill  2022 \\
\textbf{Contributed Talk}: \textit{Spatial Context of Heterogenous T Cell Response to Fungal Insult.}	\\

\noindent
International conference on machine learning. Long Beach, California, USA \hfill  2019 \\
\textbf{Contributed Talk}: \textit{Understanding and controlling memory in recurrent neural networks}	\\




\section*{TEACHING AND MENTORSHIP}

\noindent
Intern Mentor, Dana Pe'er Lab, Memorial Sloan Kettering Cancer Center\\
\textbf{Shouvik Mani}, Spatial Optimal Transport for analyzing cellular microenvironments\hfill 2022\\
\textbf{Yasa Baig}, Discrete latent models for interpretable single-cell analysis \hfill 2021\\

\noindent
Teaching Assistant, Technion - Israel Institute Of Technology, \hfill 2018-2019\\
\textbf{Introduction to Biological Systems and Signals}, Head TA \\
\textbf{Electromagnetic Fields}\\


\section*{REVIEWING}
\begin{itemize}
  \item \textbf{Journals}: Nature Biomedical Engineering, Nature Biotechnology, Cell, Genome Biology
  \item \textbf{Conferences}: NeuRIPS, ICLR, ICML, ICML Workshop in Computational Biology
\end{itemize}

% End document
\end{document}
